Light Transport Techniques for Tensor Field Visualization

### 2019-08-06 beamer2thesis/dummy.tex
update

\frame[plain]{\titlepage}
\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.6\textwidth}
  \centering
	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_base_edit.pdf}
	\caption*{Light Transport Gradient - Domain of Light Distributions}
	\end{minipage}
\end{figure}

} % END OF FRAME

\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.6\textwidth}
  \centering
	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_edit.pdf}
	\caption*{Light Transport Gradient - Domain of Light Distributions}
	\end{minipage}
\end{figure}

} % END OF FRAME

\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.5\textwidth}
  \centering
	\includegraphics[height=0.85\textwidth]{skizze/addins/grid_two_base.pdf}
	\caption*{Light Transport Gradient - Neighborhood}
	\end{minipage}
\end{figure}

} % END OF FRAME
\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.5\textwidth}
  \centering
	\includegraphics[height=0.85\textwidth]{skizze/addins/grids_two_edit.pdf}
	\caption*{Light Transport Gradient - Neighborhood}
	\end{minipage}
\end{figure}

} % END OF FRAME

>>>>

\frame[plain]{\titlepage}

\frame{
\frametitle{{Fundamentals - Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{u(x)}\|_2
$\\
{\scriptsize where $\| A\| _2 = \sqrt{\lambda_{\max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measures gradient of flow map $\nabla\mathbf{u(x)}$
	\item FTLE field responds largest where path lines diverge
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\caption*{Double Gyre Field}\bigskip
\begin{minipage}{\textwidth}
{\scriptsize a)}
\centering
\includegraphics[height=0.25\textwidth]{diverge.png}
\end{minipage}
\begin{minipage}{\textwidth}
{\scriptsize b)}
\centering
\includegraphics[height=0.25\textwidth]{ftle.png}
\caption*{a) Vector field, b) FTLE field}
\end{minipage}
\begin{minipage}{0.05\textwidth}
\centering
\source{http://tiny.cc/2zbjaz}
\end{minipage}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

%\frame{
%\frametitle{{Light Transport Gradient - Scheme}}
%\begin{figure}[t]
%\centering
%  \begin{minipage}{0.6\textwidth}
%  \centering
%	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_base_edit.pdf}
%	\caption*{Light Transport Gradient - Domain of Light Distributions}
%	\end{minipage}
%\end{figure}
%
%} % END OF FRAME
%
%\frame{
%\frametitle{{Light Transport Gradient - Scheme}}
%\begin{figure}[t]
%\centering
%  \begin{minipage}{0.6\textwidth}
%  \centering
%	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_edit.pdf}
%	\caption*{Light Transport Gradient - Domain of Light Distributions}
%	\end{minipage}
%\end{figure}
%
%} % END OF FRAME
%
%
%\frame{
%\frametitle{{Light Transport Gradient - Scheme}}
%\begin{figure}[t]
%\centering
%  \begin{minipage}{0.5\textwidth}
%  \centering
%	\includegraphics[height=0.85\textwidth]{skizze/addins/grid_two_base.pdf}
%	\caption*{Light Transport Gradient - Neighborhood}
%	\end{minipage}
%\end{figure}	
%
%} % END OF FRAME
%\frame{
%\frametitle{{Light Transport Gradient - Scheme}}
%\begin{figure}[t]
%\centering
%  \begin{minipage}{0.5\textwidth}
%  \centering
%	\includegraphics[height=0.85\textwidth]{skizze/addins/grids_two_edit.pdf}
%	\caption*{Light Transport Gradient - Neighborhood}
%	\end{minipage}
%\end{figure}
%
%} % END OF FRAME
